\documentclass[11pt]{article}
\usepackage{calc}
\usepackage{comment}
\usepackage[fixed]{fontawesome5}

\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}%
        {\begin{enumerate}{}{%
       \setlength{\leftmargin}{\bibhang}%
       \setlength{\itemindent}{-\leftmargin}%
       \setlength{\itemsep}{\bibsep}%
       \setlength{\parsep}{\z@}%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{enumerate}\vspace{-.6\baselineskip}}
\makeatother

\reversemarginpar

\usepackage[paper=letterpaper,
            marginparwidth=1.1in,
            marginparsep=.05in,
            margin=.5in,
            includemp]{geometry}

\setlength{\parindent}{0in}
\usepackage[shortlabels]{enumitem}

\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage}%
                    \hfill \,}}

\usepackage{color,hyperref}
\definecolor{darkblue}{RGB}{0,80,160}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\makeheading}[2][]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
             \vspace*{-1.0\baselineskip}% Lifted up more to prevent cutoff
             {\large \bfseries #2 \hfill #1}\\[0.05\baselineskip]%
                 \rule{\columnwidth}{1pt}%
             \vspace*{1.2\baselineskip}% Increased space after rule
         \end{minipage}}

\renewcommand{\section}[1]{\pagebreak[3]%
    \hyphenpenalty=10000%
    \vspace{1.6\baselineskip}%
    \phantomsection\addcontentsline{toc}{section}{#1}%
    \noindent\llap{\scshape\smash{\parbox[t]{\marginparwidth}{\raggedright #1}}}%
    \vspace{-\baselineskip}\par}

\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1,leftmargin=*]}{\end{itemize}%
         \vspace{-.6\baselineskip}}
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt]}
        {\end{itemize}}
\newenvironment{loneinnerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt]}
        {\end{itemize}\vspace{-.6\baselineskip}}

\newcommand{\blankline}{\quad\pagebreak[3]}
\newcommand{\halfblankline}{\quad\vspace{-0.5\baselineskip}\pagebreak[3]}

\newcommand\doilink[1]{\href{http://dx.doi.org/#1}{#1}}
\newcommand\doi[1]{doi:\doilink{#1}}
\providecommand*\url[1]{\href{#1}{#1}}
\renewcommand*\url[1]{\href{#1}{\texttt{#1}}}
\providecommand*\email[1]{\href{mailto:#1}{#1}}
\providecommand\BibTeX{{B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    \TeX}}
\providecommand\Matlab{\textsc{Matlab}}

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\makeheading{Shelvean Kapita}

\section{Contact Information}
\newlength{\rcollength}\setlength{\rcollength}{1.4in}%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
    {Department of Mathematics} & \\
    {Texas A\&M University}\\
    Blocker 328A\\
    College Station & \\
    United States of America & \\
    \faIcon{phone-square-alt}\;\; +979-845-7554 & \\
    \faIcon{envelope}\;\;\email{kapita@tamu.edu}\\
    \faIcon{link}\;\;\href{https://shelvean.github.io/math-tools}{Personal Webpage}
\end{tabular}

\section{Education}
\href{https://www.udel.edu}{\textbf{University of Delaware}},
Newark, DE, United States
\begin{outerlist}
\item[] Ph.D.,
             {Applied Mathematics},
             Aug 2016
        \begin{innerlist}
        \item Thesis Topic:
        {{Plane Wave Discontinuous Galerkin Methods for Acoustic Scattering}}
        \item Advisor:
              {Peter B. Monk}
        \end{innerlist}
\item[] M.S.,
        {Applied Mathematics},
             Aug 2012
\end{outerlist}
\vspace{.1in}
\href{https://www.lafayette.edu}{\textbf{Lafayette College}},
Easton, PA, United States
\begin{outerlist}
\item B.S. in
        {Mathematics},
A.B. in
        {Physics}, May 2010
        \begin{innerlist}
        \item \emph{Cum Laude, Honors in Mathematics}
        \item \emph{Minor in Philosophy}
        \end{innerlist}
\end{outerlist}

\section{Employment}
\href{http://www.tamu.edu}{\textbf{Texas A\&M University}}, College Station, TX, United States
\begin{outerlist}
 \item Department of Mathematics\\
 Instructional Assistant Professor, Aug 2023 - current
\end{outerlist}
\vspace{0.5cm}
\href{https://www.uz.ac.zw}{\textbf{University of Zimbabwe}}, Harare, Zimbabwe
\begin{outerlist}
 \item Department of Mathematics \& Computational Sciences \\
 Lecturer, May 2022 - Aug 2023
\end{outerlist}
\vspace{0.5cm}
\href{https://www.math.uga.edu}{\textbf{University of Georgia}}, Athens, GA, United States
\begin{outerlist}
\item Limited Term Assistant Professor, Aug 2017 - May 2020
\end{outerlist}
\vspace{0.5cm}
\href{https://www.ima.umn.edu}{\textbf{Institute for Mathematics and Its Applications}}, {University of Minnesota},
Minneapolis, MN, United States
\begin{outerlist}
\item Postdoctoral Fellow, {Mathematics and Optics }, Aug 2016 - Aug 2017.
\end{outerlist}
\vspace{0.5cm}
\href{https://www.udel.edu}{\textbf{University of Delaware}},
Newark, DE, United States
\begin{outerlist}
\item Research and Teaching Assistant, Aug 2010 - Aug 2016
\end{outerlist}

\newpage

\section{Teaching}
{\textbf{Texas A\&M University - College Station}}\\
\textbf{Instructor:}
\textbf{Spring 2026:}
\begin{itemize}
\item \href{https://www.math.tamu.edu/courses/math308/}{MATH 308} (Differential Equations)
\end{itemize}
\textbf{Fall 2025:}
\begin{itemize}
\item \href{https://www.math.tamu.edu/courses/math417/}{MATH 417} (Numerical Methods)
\item \href{https://www.math.tamu.edu/courses/math308/}{MATH 308} (Differential Equations)
\end{itemize}
\textbf{Summer 2025:}
\begin{itemize}
\item \href{https://www.math.tamu.edu/courses/math304/}{MATH 304} (Linear Algebra)
\end{itemize}
\textbf{Spring 2025:}
\begin{itemize}
\item \href{https://www.math.tamu.edu/courses/math308/}{MATH 308} (Differential Equations)
\end{itemize}
\textbf{Fall 2024:}
\begin{itemize}
\item \href{https://www.math.tamu.edu/courses/math140/}{MATH 140} (Mathematics for Business and Social Sciences)
\item \href{https://www.math.tamu.edu/courses/math147/}{MATH 147} (Calculus I for Biological Sciences)
\end{itemize}
\textbf{Summer 2024:}
\begin{itemize}
\item \href{https://www.math.tamu.edu/courses/math308/}{MATH 308} (Differential Equations)
\end{itemize}
\textbf{Spring 2024:}
\begin{itemize}
\item \href{https://www.math.tamu.edu/courses/math308/}{MATH 308} (Differential Equations)
\end{itemize}
\textbf{Fall 2023:}
\begin{itemize}
\item \href{https://www.math.tamu.edu/courses/math140/}{MATH 140} (Mathematics for Business and Social Sciences)
\item \href{https://www.math.tamu.edu/courses/math417/}{MATH 417} (Numerical Methods)
\end{itemize}
{\textbf{University of Zimbabwe}}\\
\textbf{Lecturer:}
\begin{itemize}
\item MTSCS515 (Numerical Linear Algebra and Optimization): Block C, Semester 2 2023
\item \href{https://shelvean.github.io/teach-npde}{MTSCS546} (Numerical Methods for Partial Differential Equations): Block C, Semester 1 2022
\item \href{https://shelvean.github.io/teach-pde}{HMTH407, HFM307} (Partial Differential Equations): Block B, Semester 2 2022
\item \href{https://shelvean.github.io/teach-fs}{MTE201} (Engineering Mathematics 2): Block A, Semester 2 2022
\item \href{https://shelvean.github.io/teach-na}{HMTHCS212, HFM213} (Numerical Methods, 2 sections): Block D, Semester 1 2022
\end{itemize}
{\textbf{University of Georgia}}\\
\textbf{Instructor:}
\begin{itemize}
\item \href{https://www.math.uga.edu/courses/content/math-45006500}{MATH 4500/6500} (Numerical Analysis 1): Spring 2019
\item \href{https://bulletin.uga.edu/CoursesHome?cid=902}{MATH 2700} (Elementary Differential Equations): Spring 2019
\item \href{https://www.math.uga.edu/2250}{MATH 2250} (Calculus I for Science and Engineering): Fall 2019, Fall 2018, Spring 2018, Fall 2017
\item \href{https://www.math.uga.edu/1113}{MATH 1113} (PreCalculus): Fall 2017
\end{itemize}
{\textbf{University of Delaware}}\\
\textbf{Instructor:}
\begin{itemize}
\item \href{https://catalog.udel.edu/preview_course_nopop.php?catoid=63&coid=386329}{MATH 243} (Analytic Geometry and Calculus C): Winter 2015
\item \href{https://catalog.udel.edu/preview_course_nopop.php?catoid=63&coid=386329}{MATH 221} (Calculus I for Business and Economics): Winter 2012, Winter 2013, Winter 2014
\end{itemize}
\textbf{Teaching Assistant:}
\begin{itemize}
\item \href{https://catalog.udel.edu/preview_course_nopop.php?catoid=63&coid=386329}{MATH 243} (Analytic Geometry and Calculus C Lab): Spring 2015, Fall 2012
\item \href{https://www.mathsci.udel.edu/courses-placement/foundational-mathematics-courses/math-241}{MATH 241} (Analytic Geometry and Calculus A): Fall 2010, Spring 2011, Fall 2011
\item \href{https://catalog.udel.edu/preview_course_nopop.php?catoid=63&coid=386328}{MATH 242} (Analytic Geometry and Calculus B): Spring 2012
\end{itemize}

\section{Pedagogical Tool Development}
\textbf{Interactive JavaScript Applications for Mathematics Education}\\

Developed and maintain a comprehensive suite of web-based interactive tools \\ hosted at \href{https://shelvean.github.io/math-tools}{shelvean.github.io/math-tools} to enhance student learning in undergraduate mathematics courses:

\begin{itemize}
\item \href{https://shelvean.github.io/math-tools/numerical.html}{Numerical Methods Tools}: Interactive visualizations for Newton's method (root-finding), polynomial and rational function interpolation, least squares data fitting, and finite difference approximations with error estimates.

\item \href{https://shelvean.github.io/math-tools/projects.html}{Differential Equations Visualizers}: Collection of tools for visualizing direction fields, phase line diagrams, phase portraits (linear and nonlinear systems), dynamical systems (Lotka-Volterra predator-prey, Lorenz system), mechanical systems (mass-spring-damper, forced vibrations, pendulum), potential functions, and Fourier series approximations.

\item \href{https://shelvean.github.io/math-tools/linear.html}{Linear Algebra Computational Tools}: Interactive calculators for matrix operations (product, inverse, determinants), matrix factorizations (LU, Cholesky, QR, SVD, CR), solving linear systems (REF, RREF), eigenvalue computations, matrix diagonalization, coordinate transformations, Gram-Schmidt orthogonalization, least squares methods, and visualizing the four fundamental subspaces.

\item \href{https://shelvean.github.io/math-tools/corners.html}{Linear Programming Visualizer}: Graphical solution tool for two-variable linear programming problems using the method of corners, with interactive constraint visualization and corner point evaluation.

\item \href{https://shelvean.github.io/math-tools/pdf_sort.html}{PDF Document Organizer}: Browser-based tool for combining multiple PDFs, rearranging pages via drag-and-drop, adding blank pages, and removing pages for efficient management of course materials.

\item \href{https://shelvean.github.io/math-tools/seatallocator.html}{Classroom Seating Allocator}: Automated tool for generating optimized seating arrangements in specific TAMU classrooms, maximizing spacing between students for exam administration.

\item \href{https://shelvean.github.io/math-tools/gradecalc.html}{Grade Distribution Calculator}: Statistical analysis tool supporting multiple grading schemes (US, UK) for computing grade distributions, descriptive statistics, and generating visualizations from uploaded grade data.

\item \href{https://shelvean.github.io/math-tools/timer.html}{Classroom Timer}: Display tool with local time and countdown timer modes for managing in-class activities and exam timing.
\end{itemize}

These tools have been integrated into undergraduate course instruction at Texas A\&M University and are freely available to students and educators worldwide, demonstrating commitment to accessible, technology-enhanced mathematics education.

\section{Undergraduate Thesis Supervision}
{\textbf{\hspace{1cm} Texas A\&M University}}
\begin{itemize}
    \item Samuel Hernandez Quijas '26, Honors Capstone Project: \emph{Freshman Survival Guide Video Series for Mathematics Students}
\end{itemize}

{\textbf{\hspace{1cm} University of Zimbabwe}}
\begin{itemize}
    \item \href{https://people.tamu.edu/~kapita/GeraldMunetsiFinalDissertation.pdf}{Gerald Munetsi} '23, BSc Hons in Applied Mathematics and Economics
    \item \href{https://people.tamu.edu/~kapita/TalentMarambaFinalDissertation.pdf}{Talent Maramba} '23, BSc Hons in Applied Mathematics and Economics
    \item Cosmas T. Nyazika '23, BSc Hons in Applied Mathematics and Economics
    \item Clemeo Gwezere '23, BSc Hons in Applied Mathematics and Economics
\end{itemize}

\section{Service}
\begin{itemize}
\item Spring 2026: Week in Review lead for Math 308 (Differential Equations) -- TAMU
\item Fall 2025: Week in Review lead for Math 308 (Differential Equations) -- TAMU
\item Spring 2025: Week in Review lead for Math 308 (Differential Equations) -- TAMU
\item Fall 2024: Week in Review lead for Math 140 (Mathematics for Business and Social Sciences) -- TAMU
\item Spring 2024: Week in Review lead for Math 308 (Differential Equations) -- TAMU
\item 2023 TAMU High School Math Contest, referee
\item Level 2 (sophomore) course coordinator, Mathematics Department, University of Zimbabwe
\item Computer Laboratory and Library Committee, Mathematics Department, University of Zimbabwe
\end{itemize}

\section{Computer Languages}
\begin{itemize}
\item Scientific programming: MATLAB, R, Python
\item Web programming: HTML, CSS, JavaScript
\item Database and typesetting: LaTeX, SQL
\end{itemize}

\section{Publications}
\vspace{-.1275in}
\begin{bibsection}
    \item {\bf Kapita, S.}, Monk, P., Selgas, V. `A Trefftz Discontinuous Galerkin Method for Time Harmonic
Waves with Generalized Impedance Boundary Conditions. \href{https://doi.org/10.1080/00036811.2018.1498965}{\faIcon{external-link-square-alt}} {\emph{Applicable Analysis}}, 2018.
    \item {\bf Kapita, S.}, Monk, P., A Plane Wave Discontinuous Galerkin Method with a Dirichlet-to-Neumann Boundary Condition for a Scattering Problem in Acoustics. \href{http://www.sciencedirect.com/science/article/pii/S0377042717303114}{\faIcon{external-link-square-alt}} \emph{Journal of Computational and Applied Mathematics}, 327, 208--225, 2018.
    \item {\bf Kapita, S.}, Plane Wave Discontinuous Galerkin Methods for Acoustic Scattering, \href{https://udspace.udel.edu/bitstream/handle/19716/19983/2016_KapitaShelvean_PhD.pdf?sequence=1&isAllowed=y}{\faIcon{external-link-square-alt}} \emph{Ph.D. Thesis, University of Delaware}, 2016.
    \item {\bf Kapita, S.}, Monk, P., Warburton, T., Residual based Adaptivity and PWDG Methods for the Helmholtz Equation. \href{https://doi.org/10.1137/140967696}{\faIcon{external-link-square-alt}} \emph{SIAM Journal on Scientific Computing}, 37(3): A1525--A1553, 2015.
    \item Abedin, F., Corvino, J., {\bf Kapita, S.}, and Wu, H., On Isoperimetric Surfaces in General Relativity II. \href{http://www.sciencedirect.com/science/article/pii/S0393044009001259}{\faIcon{external-link-square-alt}} \emph{Journal of Geometry and Physics}, 59(11):1453--1460, 2009.
\end{bibsection}

\section{Presentations}
\begin{itemize}
\item Seminar (online): {\emph{A Finite Element Method for Solving the Elliptic Obstacle Problem}}, Applied Mathematics \& Statistics Seminar, The Johns Hopkins University, Baltimore, MD. Jan 31, 2023.
\item Seminar: {\emph{A Bivariate Spline PML Approximation of the Exterior Helmholtz Equation}}, Applied Math Seminar, Auburn University, Auburn, AL. Feb 8, 2019.
\item Seminar: {\emph{A Bivariate Spline PML Approximation of the Exterior Helmholtz Equation}}, Applied Math Seminar, University of Georgia, Athens, GA. Feb 6, 2019.
\item Seminar: {\emph{An Adaptive PML Technique for Time Harmonic Scattering}}, Applied Math Seminar, University of Georgia, Athens, GA. April 30, 2018
\item Mini-symposium: {\emph{A Trefftz Discontinuous Galerkin Method for Time-Harmonic Waves with Generalized Impedance Boundary Conditions}}, {SIAM Conference on Analysis of Partial Differential Equations}, Hyatt Regency Baltimore Inner Harbor, Baltimore, MD. Dec 9-12, 2017.
\item Mini-symposium: {\emph{A Trefftz Discontinuous Galerkin Method for Time-Harmonic Waves with Generalized Impedance Boundary Conditions}}, {SIAM Central States Section}, Colorado State University, Fort Collins, CO. Sept 30, 2017.
\item Seminar: {\emph{A Trefftz Discontinuous Galerkin Method for Time-Harmonic Waves with Generalized Impedance Boundary Conditions}}, Applied Math Seminar, University of Georgia, Athens, GA. Sept 5, 2017.
\item Seminar: {\emph{Plane Wave Discontinuous Galerkin Methods for Acoustic Scattering}}, CCMA PDE's and Numerical Methods Seminar, Pennsylvania State University, PA. Jan 19, 2017.
\item Seminar: {\emph{Plane Wave Approximation of Homogeneous Helmholtz Solutions}}, Cockburn's Seminar, University of Minnesota, Minneapolis, MN. Dec 2016
\item Seminar: {\emph{Plane Wave Discontinuous Galerkin Methods for Acoustic Scattering}}, IMA Postdoc Seminar, University of Minnesota, Nov 22, 2016.
\item Workshop: {\emph{Plane Wave Discontinuous Galerkin Methods for Acoustic Scattering}}, NSF Mathematics Institutes' Modern Math Workshop at SACNAS, Long Beach CA. Oct 12-13, 2016.
\item Conference: {\emph{Plane Wave Discontinuous Galerkin Methods for Acoustic Scattering}}, International Conference on Computational Mathematics and Inverse Problems, On the occasion of the 60th birthday of Prof. Peter Monk, Michigan Technological University. Aug 19, 2016.
\item Workshop: {\emph{A Plane Wave Discontinuous Galerkin Method with Dirichlet-to-Neumann Boundary Conditions}}, DelMar Numerics Day, George Mason University, Fairfax VA. May 2016.
\item Symposium: {\emph{Residual based Adaptivity and PWDG Methods for the Helmholtz Equation}}, Joint Mathematics Meetings, Seattle WA. Jan 2016.
\item Poster: {\emph{Adaptive Plane Wave Discontinuous Galerkin Methods for the Helmholtz Equation}}, Franco-German Summer School, Inverse Problems for Waves, {\'E}cole Polytechnique, Palaiseau France. August 2015.
\item Symposium: {\emph{Residual based Adaptivity and PWDG Methods for the Helmholtz Equation}}, Winter Research Symposium, University of Delaware. February 2015.
\item Workshop: {\emph{Plane Wave Discontinuous Galerkin Methods for the Helmholtz Equation}}, DelMar Numerics Day, University of Maryland, Baltimore County. May 2014.
\item Seminar: {\emph{Convergence of an Interior Penalty Adaptive Discontinuous Galerkin Method,}} Hallenbeck Graduate Student Seminar, University of Delaware. April 2013.
\end{itemize}

\section{Professional Activities and Workshops}
\begin{itemize}
\item TAMU 101 New Faculty Professional Development and Networking, Sept 20 2023, Oct 11 2023
\item {Georgia Scientific Computing Symposium}, Georgia Institute of Technology, Atlanta, GA. Feb 16, 2019.
\item {SIAM Conference on Analysis of Partial Differential Equations}, Baltimore, MD. Dec 9-12, 2017.
\item {SIAM Central States Conference}, Colorado State University, Fort Collins, CO. Sept 29-Oct 1, 2017.
\item {International Conference on Computational Mathematics and Inverse Problems}, On occasion of the 60th birthday of Prof. Peter Monk, Michigan Technological University, Houghton MI. Aug 15-19, 2016.
\item {IMA PI Graduate Student Conference on Finite Element Methods for Eigenvalue Problems}, Michigan Technological University, Houghton MI. Aug 10-14, 2016.
\item {DelMar Numerics Day, George Mason University}, Fairfax VA. May 14 2016.
\item{Finite Element Circus}, University of Maryland, College Park MD. Apr 15-16, 2016.
\item {Joint Mathematics Meetings}, Seattle WA. Jan 4-7, 2016.
\item {Finite Element Circus}, University of Massachusetts, Dartmouth MA. Oct 16-17, 2015.
\item {Franco-German Summer School, Inverse Problems for Waves}, {\'E}cole Polytechnique, Palaiseau France. Aug 24-28, 2015.
\item {Mathematical Problems in Industry Workshop (MPI)}, University of Delaware, Newark DE. June 22-26 2015.
\item {Finite Element Circus}, George Mason University, Fairfax VA. Mar 27-28, 2015.
\item {DelMar Numerics Day}, University of Maryland Baltimore County, Baltimore MD. May 10, 2014.
\item {Finite Element Circus}, Wayne State University, Detroit MI. Mar 28-29, 2014.
\item Finite Element Circus, University of Delaware, Newark DE. Oct 18-19, 2013.
\item {International Conference on Novel Directions in Inverse Scattering}, Honoring David Colton, University of Delaware, Newark DE. July 29-Aug 2, 2013.
\item {DelMar Numerics Day}, University of Maryland, College Park MD. May 4, 2013.
\item {Mathematical General Relativity}, Summer Course, MSRI Berkeley CA. July 9-20, 2012.
\item {NSF-CBMS Conference on Finite Element Exterior Calculus}, Institute for Computational and Experimental Research in Mathematics (ICERM), Brown University. Jun 11-15, 2012.
\item {Joint Mathematics Meetings}, San Francisco CA. Jan 13-16, 2010.
\end{itemize}

\halfblankline

\end{document}
